Supporting online material for\\ \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127 countries}

### 2016-08-15 Documents/treatment_cascade.tex
Add references for treatment cascade table

  Australia & 90.0\% & 99.4\% & 92.5\% & \cite{Unaids2016-an}, \url{https://kirby.unsw.edu.au/sites/default/files/hiv/resources/HIVASRsuppl2014_online.pdf} \\
  Austria & 80.0\% & 86.8\% & 63.0\% & 28th Report of the Austrian HIV Cohort Study (Innsbruck, September 30th, 2015), \url{https://www.google.com/url?sa=t&rct=j&q=&esrc=s&source=web&cd=12&ved=0ahUKEwjQkqHwwtLNAhXG0h4KHYxYDdM4ChAWCB0wAQ&url=http%3A%2F%2Fdermatologie.tirol-kliniken.at%2Fdata.cfm%3Fvpath%3Ddokumente%2F2015-hiv-kohortenbericht&usg=AFQjCNH9LyCKkigHECw7oYAEq_NBfRHjKw&sig2=eywFWu8eQN6aWf_QwHNLlw&bvm=bv.125801520,d.dmo&cad=rja} \\

@@

  Belgium & 80.0\% & 74.5\% & 91.0\% & \cite{Unaids2016-an}, \url{http://ec.europa.eu/chafea/documents/health/hiv-cluster-meeting-material/presentations-pharis-s3_en.pdf}, 2015a \\

@@

  Canada & 79.0\% & 64.6\% & 68.6\% & \url{http://www.catie.ca/sites/default/files/2014-HIV-Estimates-in-Canada-EN.pdf}, \url{http://www.catie.ca/en/catienews/2014-02-19/gaps-british-columbia-s-hiv-treatment-cascade} \\

@@

  China & 64.2\% & 59.0\% & 91.0\% & \cite{Unaids2016-an, AIDSdatahub-fg}, \url{http://www.avert.org/professionals/hiv-around-world/asia-pacific/china} \\
  Colombia & 45.0\% & 73.0\% & 70.0\% & \url{http://ecdc.europa.eu/en/publications/Publications/dublin-declaration-continuum-of-care-2014.pdf} \\

@@

  Denmark & 85.0\% & 72.9\% & 95.2\% & \url{http://www.aidsmap.com/Australia-performs-best-in-HIV-treatment-cascade-62-with-undetectable-viral-load/page/2919074/} \\

@@

  Egypt & 40.6\% & 56.5\% & 80.0\% & \url{http://english.alarabiya.net/en/perspective/analysis/2014/08/28/Registered-HIV-AIDS-cases-rising-in-Egypt-U-N-.html}, 2015b \\

@@

  Estonia & 87.0\% & 33.3\% & 65.5\% & \url{https://www.sm.ee/sites/default/files/content-editors/eesmargid_ja_tegevused/Tervis/Tervislik_eluviis/who_raport_hiv_aids_treatment_and_care_in_estonia.pdf} \\
  Ethiopia & 71.5\% & 70.0\% & 82.0\% & \cite{Unaids2016-am}, \url{https://dhsprogram.com/pubs/pdf/CR30/CR30.pdf}, 2012b \\
  France & 81.0\% & 91.4\% & 70.3\% & \url{http://www.aidsmap.com/Australia-performs-best-in-HIV-treatment-cascade-62-with-undetectable-viral-load/page/2919074/} \\

@@

  Italy & 70.0\% & 87.6\% & 62.4\% & \url{https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4348082/} \\

@@

  Netherlands & 73.0\% & 93.2\% & 89.8\% & \url{http://www.aidsmap.com/Australia-performs-best-in-HIV-treatment-cascade-62-with-undetectable-viral-load/page/2919074/} \\

@@

  Russia & 49.0\% & 23.5\% & 80.0\% & \url{http://www.jiasociety.org/index.php/jias/article/view/19506} \\

@@

  Sweden & 90.0\% & 92.1\% & 94.7\% & \url{http://www.croiconference.org/sessions/swedish-hiv-treatement-cascade} \\
  Switzerland & 80.9\% & 87.8\% & 96.3\% & \url{http://www.natap.org/2015/IAS/Jake_IAS_Slides_July20X.pdf} \\

@@

  United Kingdom & 82.5\% & 89.8\% & 94.7\% & \url{https://www.gov.uk/government/uploads/system/uploads/attachment_data/file/477702/HIV_in_the_UK_2015_report.pdf} \\
  United States & 87.0\% & 52.0\% & 81.9\% & \url{http://www.cdc.gov/hiv/pdf/surveillance_Report_vol_19_no_3.pdf}, \url{http://www.cdc.gov/hiv/statistics/overview/geographicdistribution.html} \\

>>>>

  Australia & 90.0\% & 99.4\% & 92.5\% & \cite{Unaids2016-an, kirby2014}  \\
  Austria & 80.0\% & 86.8\% & 63.0\% & \cite{ahivcos2015} \\

@@

  Belgium & 80.0\% & 74.5\% & 91.0\% & \cite{Unaids2016-an,europa2012}, 2015a \\

@@

  Canada & 79.0\% & 64.6\% & 68.6\% & \cite{catie2014a,catie2014b} \\

@@

  China & 64.2\% & 59.0\% & 91.0\% & \cite{Unaids2016-an, AIDSdatahub-fg, avert2013} \\
  Colombia & 45.0\% & 73.0\% & 70.0\% & \cite{ecdc2014} \\

@@

  Denmark & 85.0\% & 72.9\% & 95.2\% & \cite{aid2014} \\

@@

  Egypt & 40.6\% & 56.5\% & 80.0\% & \cite{alarab2014} 2015b \\

@@

  Estonia & 87.0\% & 33.3\% & 65.5\% & \cite{chip2014}  \\
  Ethiopia & 71.5\% & 70.0\% & 82.0\% & \cite{Unaids2016-am, usaid2013}, 2012b \\
  France & 81.0\% & 91.4\% & 70.3\% & \cite{aid2014} \\

@@

  Italy & 70.0\% & 87.6\% & 62.4\% & \cite{camoni2015estimating}  \\

@@

  Netherlands & 73.0\% & 93.2\% & 89.8\% & \cite{aid2014} \\

@@

  Russia & 49.0\% & 23.5\% & 80.0\% & \cite{pokrovskaya2014cascade} \\

@@

  Sweden & 90.0\% & 92.1\% & 94.7\% & \cite{croi2016} \\
  Switzerland & 80.9\% & 87.8\% & 96.3\% & \cite{ias2015} \\

@@

  United Kingdom & 82.5\% & 89.8\% & 94.7\% & \cite{ukhIv2015} \\
 United States & 87.0\% & 52.0\% & 81.9\% & \cite{cdc2012a,cdc2014} \\
